Person with advantage functionality for `hyper3` objects: `pwa3()`

### 2025-12-08 inst/pwa3.Rmd
another example

>>>>

# Yet another example {-}

Here we consider help in turn to each of five competitors.  From the
function below, if someone gets help they generally do quite well.

```{r lam4def}

lam4 <- function(x, givelike=FALSE){
    race_help <- 
        myr(3,1,2,4,5) |> pwa3(a=x) +
        myr(2,3,1,4,5) |> pwa3(b=x) +
        myr(3,1,5,4,2) |> pwa3(c=x) +
        myr(4,2,5,3,1) |> pwa3(d=x) +
        myr(3,5,2,4,1) |> pwa3(e=x)
    if(givelike){
        return(race_help)
    } else {
        return(maxp(race_help, give=TRUE)$value)
    }
}
```

```{r calclam4, cache=TRUE}
l <- exp(seq(from= -0.5, to=log(250), len=15))
like4 <- sapply(l,lam4)
```

```{r optimizelamf4, cache=TRUE}
optimal_sol4 <- optimize(lam4, exp(2:3), maximum=TRUE)
```

It makes sense to consider our likelihood function at the estimate for
$\lambda$:

```{r maxp4}
H <- lam4(optimal_sol4$maximum, givelike=TRUE)
H
summary(H)
maxp(H)
```

Above we see that the evaluate is very high for `c` having a BT
strength of about 0.6.  This is consistent with our observations for
twice we see `c` winning [that is, coming first] without any help.

```{r plotlam4}
plot(log(l),like4-max(like4), type="b", pch=16)
abline(h=c(0,-2), col='gray')
abline(v=0, lty=2)
abline(v = log(optimal_sol4$maximum))
```
